Theory of surface second-harmonic generation for semiconductors including effects of nonlocal operators

### 2015-01-08 reply/referees.tex
for Valerie and Nicolas

From prb@aps.org Wed Dec 17 09:19:00 2014
Date: Tue, 16 Dec 2014 21:23:48 -0500
From: prb@aps.org
To: bms@cio.mx
Subject: {Spam?} Your_manuscript BZ12227 Anderson

>>>>

From prb@aps.org Mon Dec 22 13:48:36 2014
Date: Tue, 16 Dec 2014 21:23:48 -0500
From: prb@aps.org
To: bms@cio.mx
Subject: {Spam?} Your_manuscript BZ12227 Anderson

### 2015-01-08 sent-1/manuscript.tex
for Valerie and Nicolas

We will look for the expectation value of the microscopic current density, 
$\mathbf{J}$, given by 
\begin{equation*}
\mathbf{J} = \langle{\mathbf{J}}\rangle 
           = \frac{e}{A}\mbox{Tr}({\rho}\dot{\mathbf{r}}),
\end{equation*}
where $\dot{\mathbf{r}}$ is the time derivative of the position operator of the
electron with charge $e$, defined as
\begin{equation}
\mathbf{v}\equiv \dot{\mathbf{r}}=\frac{1}{i\hbar }[\mathbf{r},H_0],  
\label{mv}
\end{equation}
with $\mathbf{v}$ the velocity operator of the electron, and $A$ the
area of the unit cell. We calculate the polarization density 
$\mathbf{P}$, related to $\mathbf{J}$ by
$\mathbf{J}=d\mathbf{P}/dt$. For a 
perturbing electromagnetic field, $\mathbf{E}(t)=
\mathbf{E}(\omega )e^{-i\tilde{\omega} t}+c.c.$,
where $\tilde\omega=\omega+i\eta $,
and $\eta >0$ adiabatically switches on the interaction,
we write the second-order nonlinear
polarization as, 
\begin{equation}
{\mathbf{\cal P}}^{\mathrm{a}}(2\omega)=
\chi^{\mathrm{a}\mathrm{b}\mathrm{c}}(-2\omega;\omega,\omega)
E^{\mathrm{b}}(\omega)E^{\mathrm{c}}(\omega),  
\label{pshg}
\end{equation}
where $\chi^{\mathrm{a}\mathrm{b}\mathrm{c}}(-2\omega ;\omega ,\omega )$ is the nonlinear
susceptibility responsible for surface second-harmonic generation
(SSHG). 
The 
superscripts in Eq.~\eqref{pshg} denote Cartesian components, and if
repeated are to be summed over. Without loss of generality we will
define $\chi^{\mathrm{a}\mathrm{b}\mathrm{c}}(-2\omega;\omega,\omega)$
 to satisfy intrinsic permutation
symmetry, 
$\chi^{\mathrm{a}\mathrm{b}\mathrm{c}}(-2\omega ;\omega ,\omega )
=\chi^{\mathrm{a}\mathrm{b}\mathrm{c}}(-2\omega ;\omega,\omega )$.

>>>>

We will look for the expectation value of the microscopic current density, 
$\mathbf{J}$, given by 
\begin{equation*}
\mathbf{J} = \langle{\mathbf{J}}\rangle 
           = \frac{e}{A}\mbox{Tr}({\rho}\dot{\mathbf{r}}),
\end{equation*}
where $\dot{\mathbf{r}}$ is the time derivative of the position operator of the
electron with charge $e$, defined as
\begin{equation}
\mathbf{v}\equiv \dot{\mathbf{r}}=\frac{1}{i\hbar }[\mathbf{r},H_0],  
\label{mv}
\end{equation}
with $\mathbf{v}$ the velocity operator of the electron, and $A$ the
area of the unit cell. We calculate the polarization density 
$\mathbf{P}$, related to $\mathbf{J}$ by
$\mathbf{J}=d\mathbf{P}/dt$. For a 
perturbing electromagnetic field, $\mathbf{E}(t)=
\mathbf{E}(\omega )e^{-i\tilde{\omega} t}+c.c.$,
where $\tilde\omega=\omega+i\eta $,
and $\eta >0$ adiabatically switches on the interaction,
we write the second-order nonlinear
polarization as, 
\begin{equation}
{\mathbf{\cal P}}^{\mathrm{a}}(2\omega)=
\chi^{\mathrm{a}\mathrm{b}\mathrm{c}}(-2\omega;\omega,\omega)
E^{\mathrm{b}}(\omega)E^{\mathrm{c}}(\omega),  
\label{pshg}
\end{equation}
where $\chi^{\mathrm{a}\mathrm{b}\mathrm{c}}(-2\omega ;\omega ,\omega )$ is the nonlinear
susceptibility responsible for surface second-harmonic generation
(SSHG). 
The 
superscripts in Eq.~\eqref{pshg} denote Cartesian components, and if
repeated are to be summed over. Without loss of generality we will
define $\chi^{\mathrm{a}\mathrm{b}\mathrm{c}}(-2\omega;\omega,\omega)$
 to satisfy intrinsic permutation
symmetry, 
$\chi^{\mathrm{a}\mathrm{b}\mathrm{c}}(-2\omega ;\omega ,\omega )
=\chi^{\mathrm{a}\mathrm{c}\mathrm{b}}(-2\omega ;\omega,\omega )$.
